\section{Mathematical Appendix}

This appendix collects all major equations used or derived in the WTF framework.

\subsection{Core Equation}

The fundamental relation between energy, time, and field localization:

\[
E = t \cdot g
\]

Where:
\begin{itemize}
    \item \( E \) — energy (observable work),
    \item \( t \) — moment of time (when the work is performed),
    \item \( g \) — field vector (location in the active field topology).
\end{itemize}

\subsection{Mass as Work Quotient}

\[
m = \frac{E}{c^2} = \frac{t \cdot g}{c^2}
\]

Mass is interpreted as the amount of work stored or maintained in the field per unit of rest-frame energy.

\subsection{Decay Probability}

The likelihood of particle decay is inversely related to the continuity of work in its local field:

\[
P_{\text{decay}} \sim 1 - \exp\left(-\frac{t \cdot g}{\tau}\right)
\]

Where \( \tau \) is the field-resonant decay threshold (energy-time product for stability).

\subsection{Tunneling Phase Leakage}

For a particle approaching a potential barrier:

\[
P_{\text{tunnel}} \propto \exp\left(-\frac{W}{t \cdot g_{\text{leak}}}\right)
\]

Where:
\begin{itemize}
    \item \( W \) — work required to sustain across the barrier,
    \item \( g_{\text{leak}} \) — effective field coherence vector in forbidden region.
\end{itemize}

\subsection{Stability Corridor for Isotopes}

Assuming field density limits on the neutron/proton balance:

\[
1.0 \leq \frac{N}{Z} \leq 1.6 \quad \text{(Full field allowance)}
\]
\[
1.1 \leq \frac{N}{Z} \leq 1.45 \quad \text{(Earth-local field)}
\]

Where \( N \) — number of neutrons, \( Z \) — number of protons.

\subsection{Field-Collapse Work Balance}

To estimate collapse potential for dense objects (e.g. black holes or jump fields):

\[
W_{\text{critical}} = t_{\text{res}} \cdot g_{\text{max}}
\]

Where \( t_{\text{res}} \) — resonance span (lifetime), and \( g_{\text{max}} \) — maximum field density before collapse.

\subsection{Graviton Work per MeV}

For isotopic transitions, the average number of “graviton units” per MeV of transition energy:

\[
G = \frac{E_{\text{MeV}}}{\varepsilon_g}
\]

Where \( \varepsilon_g \) — local energy density unit per graviton. This is approximated from stable-to-unstable decay shifts.

