\section{Comparison with Existing Theories}

\subsection{Emergent Gravity and Entropic Gravity}

Approaches by Verlinde, Jacobson, Padmanabhan, and others propose that gravity is not fundamental, but emerges from entropy or statistical effects.

\textbf{WTF distinction:}
\begin{itemize}
    \item WTF does not derive gravity from entropy;
    \item It treats gravity as a redistribution of localized field work;
    \item There is no need for holographic duality or thermodynamic abstractions.
\end{itemize}

\subsection{Quintessence and Dark Energy Models}

Scalar-field models like quintessence attempt to explain accelerated expansion via evolving energy fields.

\textbf{WTF reinterpretation:}
\begin{itemize}
    \item WTF proposes the universe is not expanding, but \textit{collapsing in phase};
    \item “Dark energy” is the field’s own background work supporting the remaining observable structure;
    \item The observed 67\% “dark energy” closely matches the theoretical exhaustion margin.
\end{itemize}

\subsection{Quantum Field Theory and Higgs Formalism}

The Higgs mechanism explains particle masses through interaction with a scalar field.

\textbf{WTF reinterpretation:}
\begin{itemize}
    \item Mass is not a result of “coupling” with a background field;
    \item It is a byproduct of temporal + spatial work committed to hold a state in the field;
    \item The Higgs field may be a special region of WTF with zero phase offset.
\end{itemize}

\subsection{String Theory and Brane Worlds}

String and brane theories attempt to model all forces by vibrational modes in multidimensional topologies.

\textbf{WTF stance:}
\begin{itemize}
    \item WTF requires no extra dimensions;
    \item The field is not a “string”, but a directional network of work threads;
    \item “Massless” and “massive” particles are not different string modes, but different phase balances.
\end{itemize}

\subsection{Summary Table}

\begin{center}
\begin{tabular}{|l|c|c|}
\hline
\textbf{Feature} & \textbf{Mainstream View} & \textbf{WTF Interpretation} \\
\hline
Mass & Coupling to Higgs & Work in time-space field \\
Gravity & Curvature of spacetime & Redistribution of local work \\
Dark Energy & Vacuum pressure & Exhausted structural field \\
Tunneling & Probabilistic overlap & Phase leakage from work imbalance \\
Stable Isotopes & Nuclear shell model & Energy allowed by field density \\
\hline
\end{tabular}
\end{center}
